An Improved ANS Transaction Template

### 2018-01-26 paper.tex
update

As explain previously, the goal of this work is to assess the rate of the HEU
production using enrichment cascade designed within the JCPOA agreement
constrains. For this work two different cases will be investigated and compare
to the reference case.

\subsection{Reference Case}
The reference case corresponds to a cascade design include all the 5060
centrifuges available within JCPOA targeting an enriched product at $90\%$ of U-235,
stripping the tail product up to 0.28 $\%$ from a feed of natural uranium. 
The design cascade in this case, includes 4 stripping stages, and 38 enriching
stages. The Feed/Product/Tail (F/P/T) assay are respectively
0.0071/0.903/0.0028.

\subsection{Case 1}
The case 1 is design to allow configure 30 cascades in the scenario (limit of
the JCPOA agreement), all design the same way. The design properties are:\\
- less than 169 centrifuges per cascade,\\
- F/P/T assays: 0.0071/0.035/0.003.\\
The corresponding design is:\\
- 167 centrifuges,\\
- F/P/T assays: 0.0071/0.0412842/0.00290548.\\

\subsection{Case 2}
The case 2 is design is also limited to 30 cascades in the scenario (limit of
the JCPOA agreement), all design the same way. In thsi case the explored design
aims to reproduce the different stage of the reference case over the different
level of cascade enrichment: the goal is to have the tails assay of a stage to
match the feed assay of the previous stage. To do so instead of aiming for a
S/E stages of 4/10, a S/E stages repartition of 6/7 was targeted.:w

@@

>>>>

As explain previously, the goal of this work is to assess the rate of the HEU
production using enrichment cascade designed within the JCPOA agreement
constrains. For this work two different cases will be investigated and compare
to the reference case.
i
\subsection{the studied cases}
\subsubsection{Reference Case}
The reference case corresponds to a cascade design include all the 5060
centrifuges available within JCPOA targeting an enriched product at $90\%$ of U-235,
stripping the tail product up to 0.28 $\%$ from a feed of natural uranium. 
The design cascade in this case, includes 4 stripping stages, and 38 enriching
stages. The Feed/Product/Tail (F/P/T) assay are respectively
0.0071/0.903/0.0028.

\subsubsection{Case 1}
The case 1 is design to allow configure 30 cascades in the scenario (limit of
the JCPOA agreement), all design the same way. The design properties are:\\
- less than 169 centrifuges per cascade,\\
- F/P/T assays: 0.0071/0.035/0.003.\\
The corresponding design is:\\
- 167 centrifuges,\\
- F/P/T assays: 0.0071/0.0412842/0.00290548.\\

\subsubsection{Case 2}
The case 2 is design is also limited to 30 cascades in the scenario (limit of
the JCPOA agreement), all design the same way. In thsi case the explored design
aims to reproduce the different stage of the reference case over the different
level of cascade enrichment: the goal is to have the tails assay of a stage to
match the feed assay of the previous stage. To do so instead of aiming for a
S/E stages of 4/10, a S/E stages repartition of 6/7 was targeted.:w

@@

\subsection{the simulation}
The simulation is build to layer up the different cascade in order to produce
HEU. The different layers of cascade will be called levels in the following. The
first task has been to determine the number of level required to produce HEU.
The optimum number of cascade per level is determine (the same way) that the
centrifuges are distributed on the different cascade stages.
Once both the number of levels and the number of cascades per level is
determined, the simulation is ran.
